
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\setlength{\footskip}{4.08003pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{ \vspace{-4pt}\scshape\raggedright\large
  }{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{ \textbf{#1}{: #2 \vspace{-2pt}} } }

\newcommand{\resumeSubheading}[4]{ \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r} \textbf{#1} & #2
      \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt} }



\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------------- \hrule 
\begin{center}
    \textbf{\huge \scshape Sebastian Kusch}\\
    \vspace{0.5cm}
    \textit{\large Quellenstraße 51, 1100 Vienna, Austria}
\end{center}
\centering
\begin{tabular*}{0.7\textwidth}{l@{\extracolsep{\fill}}r} Nationality: German &
    Email : \href{mailto:bastikusch@live.com}{bastikusch@live.com} \\
    Date of Birth: Oct 21st, 1993 & Mobile : +436705537653
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart \resumeSubheading {Ph.D., Network Science
    (Currently)}{Vienna, Austria} {Central European University, Vienna}{Oct.
    2022 -- Present} \resumeItemListStart \resumeItem{Topic}{"Disentangling
    Co-Existing Network Generating Mechanisms"} \resumeItem{Supervised by}{Tiago
    Peixoto}\resumeItemListEnd \resumeSubheading {M.Sc., Environmental
    Modelling}{Oldenburg, Germany} {Carl von Ossietzky University of
    Oldenburg}{Oct. 2018 -- May. 2022} \resumeItemListStart
    \resumeItem{Thesis}{"Steady State Solutions of Evolutionary and
    Interaction-based Multi-Layer Spreading Processes"}\resumeItem{Supervised
    by}{Thilo Gross, Jan Freund}\resumeItemListEnd \resumeSubheading {B.Sc.,
    Simulation Technology}{Stuttgart, Germany} {University of Stuttgart}{Oct.
    2013 -- May. 2017} \resumeItemListStart \resumeItem{Thesis}{"Modelling and
    Simulation of Muscle Hypertrophy, Fatigue and Maximum Force Increase in
    Performance-oriented Training"}\resumeItem{Supervised by}{Syn Schmitt,
    Daniel Häufle}\resumeItemListEnd \resumeSubHeadingListEnd


%-----------Academia-----------------

\section{Research Interests}
  \resumeSubHeadingListStart \resumeSubItem{Network Science} {Network Inference,
    Network Reconstruction, Network Algorithms.} \resumeSubItem{Complex Systems}
    {Statistical Physics, Algorithmic Information Theory, Emergence.}
    \resumeSubItem{Data Science} {Bayesian Inference, Machine Learning, Data
    Compression.} \resumeSubHeadingListEnd

\section{Research Experience}
  \resumeSubHeadingListStart

    \resumeSubheading {Research Internship}{Oldenburg, Germany} {Helmholtz
    Institute for Functional Marine Biodiversity}{Mar. 2020 -- Jul. 2020}
    \resumeItemListStart \resumeItem{Biodiversity Theory} {Using diffusion maps
    to find patterns in ecological models and data sets, scientific report
    titled "Functional patterns in ecological systems"} \resumeItem{Mathematical
    Modelling} {Using the Julia language to model ecological systems(food webs,
    competition models) and run dynamical simulations and algorithms
    (non-official Julia package at
    \href{https://github.com/bastikusch/DiffusionMap.jl}{DiffusionMap.jl})}
    \resumeItemListEnd

    \resumeSubheading {Research Internship}{Oldenburg, Germany} {BTC Business
    Technology Consulting AG / Team Data Science and Artificial
    Intelligence}{Nov. 2019 -- Feb. 2020} \resumeItemListStart
    \resumeItem{Programming Project} {Title: "Conception and implementation
    of a testing environment for an artificial intelligent system in the
    context of autonomous driving".} \resumeItem{Reinforcement Learning Project}
    {Title: "Conception and implementation of an
    artificial intelligent reinforcement learning agent with the purpose of
    driving autonomously".} \resumeItemListEnd

    \resumeSubheading {Student Research Assistant}{Oldenburg, Germany}
    {Institute for Chemistry and Biology of the Marine Environment, University
    Oldenburg}{Mar. 2019 -- Jan. 2020} \resumeItemListStart
    \resumeItem{Non-linear Dynamics Project}{ Attractor Reconstruction in Julia}
    \resumeItem{Visualization Project} {Web based visualization of bird migration
    models, written in JavaScript and HTML (see \href{https://github.com/bastikusch/birdmigration}{github.com/bastikusch/birdmigration})} \resumeItemListEnd

    \resumeSubheading {Student Research Assistant}{University Stuttgart,
    Germany} {Institute for Sports and Movement, University of Stuttgart}{Jul.
    2015 -- Nov. 2016} \resumeItemListStart \resumeItem{Biomechanics Project}{Research
    projects addressing biomechanical modelling and simulations (data
    aggregating experiments and programming in Matlab).} \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Teaching Experience}
  \resumeSubHeadingListStart

    \resumeSubheading {Certificate of Teaching in Higher Education}{Vienna,
    Austria} {Yehuda Elkana Center, CEU, Vienna}{Sep. 2023 -- Jun. 2024}
    \resumeItemListStart \resumeItem{Certificate [16 ECTS]}{Teaching program
    integrating scholarship, practice, and innovation in teaching, equipping
    participants to design effective courses, master student-centered teaching
    techniques, and assess student learning. Additional focus on utilizing
    technology, promoting diversity and inclusion, and fostering lifelong
    professional development through reflective practices.} \resumeItemListEnd

    \resumeSubheading {Teaching Assistant}{Vienna, Austria} {Central European
    University}{} \resumeItemListStart \resumeItem{Multivariate Calculus (Spring
    24)}{Weekly tutorial sessions, additional Q\&A sessions, design and grade
    assignments.} \resumeItem{Introduction to Optimization (Winter
    23/24)}{Supervise and grade group presentations, office hours, design and
    grade assignments.} \resumeItem{Numerical Methods in Calculus and Algebra
    (Fall 23/24)}{Supervise and grade group presentations, office hours, design
    and grade assignments.} \resumeItemListEnd

    \resumeSubheading {Teaching Assistant}{Stuttgart, Germany} {University of
    Stuttgart}{} \resumeItemListStart \resumeItem{Engineering Mechanics 2
    (Summer 15)}{Weekly tutorial group, Correct exercises, Assist in grading the
    final exam.} \resumeItem{Engineering Mechanics 1 (Winter 14/15)}{Weekly
    tutorial group, Correct exercises, Assist in grading the final exam.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd





  \section{Awards \& Honors}
  \resumeSubHeadingListStart \resumeSubItem{Best talk by an early career
    researcher} {NetSci 2024, Quebec} \resumeSubItem{Academic Achievement Award
    for First-Year Doctoral Students 2023/24} {CEU, Vienna}
    \resumeSubHeadingListEnd

  \section{Community Service and Outreach}
  \resumeSubHeadingListStart

    \resumeSubheading {\href{https://www.netplace.site/about}{NetPLACE Seminars}}{}
      {Organiser}{Sep. 2023 -- Present} \resumeItemListStart
      \resumeItem{Online Seminars} {Co-organize bi-weekly online seminars,
      focusing on early career researchers and the problems they encounter in
      academia.} \resumeItem{Panel, NetSci-X 2024, Venice} {Co-organized a panel with
      the title
      \href{https://sites.google.com/view/netplace/panelsconferences/netscix2024?authuser=0}{"Redefining
      scientific communication: from the scientific community to the society"} }
      \resumeItemListEnd

  \resumeSubHeadingListEnd



%-----------Non-Academia-----------------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading {Developer}{Oldenburg, Germany} {BTC Business Technology
    Consulting AG / Team Data Science and Artificial Intelligence}{Mar. 2020 --
    Jun. 2021} \resumeItemListStart \resumeItem{AI Projects}{geometric
    optimization of lane reconstructions, quantification of simulation
    uncertainties, heuristic search algorithms for dimension reduction problems
    and conception of metric search tree data structures.} \resumeItemListEnd

    \resumeSubheading {European Voluntary Service}{Galway, Ireland} {Youth Work
    Ireland Galway, YWIG}{Oct. 2017 -- Aug. 2018}


    \resumeSubheading {Voluntary Social Year}{Frankfurt, Germany} {FRAPORT
    SKYLINERS e.V.}{Aug. 2012 -- Jul. 2013}

  \resumeSubHeadingListEnd




%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart \resumeSubItem{Languages} {German (native), English
    (fluent), French, Spanish, Swedish (all basic)}

   \resumeSubItem{Programming} {Python, Julia, C\#, HTML, JavaScript, Latex,
   Git} \resumeSubHeadingListEnd

   \vfill
\begin{center}
    \raggedleft \textbf{Updated:} \today
\end{center}


%-------------------------------------------
\end{document}
